\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/iteration1.tex
add more description for i1

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. Afterward, participants were asked to complete a survey of primarily open-ended \changes{questions} about their experience.

>>>>

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. \changes{At the beginning of each acquisition, participants were asked to stand at a fixed position approximately 10-12 feet away from the nodes. They would have to look down until the target is given. As the start to connect, they may move around if they decided it would help them select. After each task, they needed to move back to the starting position.} Afterward, participants were asked to complete a survey of primarily open-ended \changes{questions} about their experience.
